\subsection{Background}
At present context of time, the rapid advancements in mobile camera technology and the widespread use of social media platforms have made it easier than ever to create and share digital pictures. Deep learning has played a crucial role in developing technologies that were previously unimaginable. One notable example is modern generative models, which can produce highly realistic images, speech, music, and video. These models have been applied in various fields, such as enhancing accessibility through text-to-speech technology and generating training data for medical imaging.
\\
\\
There will always be drawbacks to any technological breakthrough. Since deepfakes are still relatively new and expanding quickly, their excessive use as a result of rising human interest has resulted in misuse of this technology. It is simple for widespread false information to proliferate among the populace when there is no controlling element and a weak mechanism in place to identify deep fakes.Since their initial emergence in late 2017, a variety of open-source deep fake generation techniques and tools have appeared, resulting in an increase in the amount of synthetic media clips. Others may be destructive to people and society, even though many are probably intended to be amusing. Due to the accessibility of editing tools and the strong demand for topic expertise, false digital contents have been growing in number and in realism up until recently.
\\
\\
Deep fakes are now widely disseminated on social media platforms, which encourages spamming and the spread of false information. Just picture a deep fake image of Donald Trump getting arrested which was trending on twitter or a deep fake of a well-known celebrity assaulting their supporters.
These types of misinformation can brainwash the audience and are awful and endanger and mislead the general public.
\\
\\
Deep fake detection plays a crucial part in overcoming such a circumstance. Therefore, we provide a novel deep learning-based method that can successfully separate artificial intelligence-generated fake contents from authentic digital materials. In order to identify deep fakes and stop them from spreading across the internet, it is crucial to develop technology that can detect deepfakes.