\subsection{Organization of Project Report}
\begin{itemize}
    \item Copyright: Acknowledgement of copyright information.
    \item Declaration: Formal declaration of originality of our project.
    \item Acknowledgement: Expression of gratitude for the support and assistance received during our project.
    \item Abstract: Includes the concise summary of our report.
    \item Introduction:\\
    Explanation on introduction to our project.
      \begin{itemize}
        \item Background: Presentation of the background information related to deepfake generation and detection.
        \item Motivation: Mention of our motivation behind choosing deepfake detection as our project.
        \item Problem Statement: Clear definition of the problem of deepfake content and the need for reliable detection.
        \item Objectives: Outline of the specific goals and objectives of our project.
        \item Scope: Definition of the boundaries of the project based on advantages and limitations.
        \item Potential Application: Exploration of potential real-world applications our system.
        \item Originality of Project: Highlighting of the unique aspects our project.
        \item Organization of Project Report: Overview of how the report is structured.
      \end{itemize}
    \item Literature Review:\\
        Review on the research papers, articles and works studied for the project.
      \begin{itemize}
        \item Existing Systems: Discussion of relevant existing systems for deepfake detection, including Deepware and DuckDuckGoose.
        \item Developed System: Description of the key features and components of our  developed system.
      \end{itemize}
    \item Feasibility Study:
      \begin{itemize}
        \item Economic Feasibility: Assessment of the economic viability of implementing the deepfake detection system.
        \item Operational Feasibility: Examination of the practicality and operational aspects of deploying the system.
        \item Technical Feasibility: Evaluation of the technical feasibility, considering the required technologies and resources.
      \end{itemize}
    \item Methodology:
      \begin{itemize}
        \item Software Development Life Cycle: Explanation of the chosen software development life cycle for the project.
        \item Deepfake: Definition of what deepfake is and its relevance to our project.
        \item Key Features Extraction: Explanation of the process of extracting key features, including abnormal patterns.
        \item Vision Transformer Architecture: Explanation the architecture.
        \item Benefits of Vision Transformer: Advantages of using Vision Transformer.
        \item Mathematical Modeling: Explanation of mathematical components such as activation function, loss function, and others involved.
        \item Dataset Collection: Collecting and preparing datasets for training and testing.
        \item Preprocessing: Outline of the preprocessing steps, including resize, augmentation, and normalization.
        \item Face Alignment Integration: Description of the integration of face alignment into the system.
        \item Algorithm: Presentation of our algorithm.
        \item Working Description: Elaborated explanation on our model.
        \item Model Training and Testing: Details of the process of training and testing of our model.
        \item Application Development: Description of the development of the mobile app, including frontend and backend components.
      \end{itemize}
      \item Block Diagrams:
      \begin{itemize}
        \item Use Case Diagram: Visual representation of the use cases.
        \item Sequence Diagram: Illustration of the sequence of interactions within the system.
        \item Dataflow Diagram: Presentation of the flow of data within the system.
        \item Class Diagram: Display of the class structure and relationships.
        \item Activity Diagram: Illustration of the workflow and activities within the system.
      \end{itemize}
  
    \item Result and Analysis:
      \begin{itemize}
        \item Parameters: Specification of the parameters used for the deepfake detection system.
        \item Evaluation: Presentation of the evaluation metrics and results.
        \item UI of Project: Showcase of the user interface of the developed mobile app.
      \end{itemize}
  
    \item Expected Outcomes:
      \begin{itemize}
        \item Discussion of the anticipated outcomes and impacts of our system.
      \end{itemize}
  
    \item Appendices:
      \begin{itemize}
        \item Inclusion of any additional information and supplementary materials.
      \end{itemize}
  \end{itemize}

