\include{commands}
\begin{document}


\include{0ACover/1title}
\include{0ACover/0cover}

\newpage

\include{0HAbstract/abstract}
\newpage


\tableofcontents
\thispagestyle{empty}
\newpage
\listoffigures
\newpage
\include{0IAbbreviations/abbreviations}

\include{1Introduction/introduction}
\newpage



\subsection{Background}
At present context of time, the rapid advancements in mobile camera technology and the widespread use of social media platforms have made it easier than ever to create and share digital pictures. Deep learning has played a crucial role in developing technologies that were previously unimaginable. One notable example is modern generative models, which can produce highly realistic images, speech, music, and video. These models have been applied in various fields, such as enhancing accessibility through text-to-speech technology and generating training data for medical imaging.
\\
\\
There will always be drawbacks to any technological breakthrough. Since deepfakes are still relatively new and expanding quickly, their excessive use as a result of rising human interest has resulted in misuse of this technology. It is simple for widespread false information to proliferate among the populace when there is no controlling element and a weak mechanism in place to identify deep fakes.Since their initial emergence in late 2017, a variety of open-source deep fake generation techniques and tools have appeared, resulting in an increase in the amount of synthetic media clips. Others may be destructive to people and society, even though many are probably intended to be amusing. Due to the accessibility of editing tools and the strong demand for topic expertise, false digital contents have been growing in number and in realism up until recently.
\\
\\
Deep fakes are now widely disseminated on social media platforms, which encourages spamming and the spread of false information. Just picture a deep fake image of Donald Trump getting arrested which was trending on twitter or a deep fake of a well-known celebrity assaulting their supporters.
These types of misinformation can brainwash the audience and are awful and endanger and mislead the general public.
\\
\\
Deep fake detection plays a crucial part in overcoming such a circumstance. Therefore, we provide a novel deep learning-based method that can successfully separate artificial intelligence-generated fake contents from authentic digital materials. In order to identify deep fakes and stop them from spreading across the internet, it is crucial to develop technology that can detect deepfakes.

\newpage


\subsection{Problem Statement}
With the help of visual effects, convincing modifications of digital photographs and videos have been proven for many years. However, new developments in deep learning have dramatically increased the realism of fake content and made it more widely available.   These purportedly artificial intelligence-generated works of media are also known as "deepfakes". It is easy to create deep fakes utilizing artificial intelligence techniques. However, it is extremely difficult to identify these Deep Fakes. In the past, there have been numerous instances of deep fakes being used to effectively incite political unrest, stage terrorist attacks, blackmail individuals, etc. Therefore, it becomes crucial to identify these deep fakes and stop their spread through social media. Therefore, with the growing curiosity we have taken a
step forward in detecting the deep fakes using vggface2 based artificial neural network.
\newpage


\include{1Introduction/objectives}
\newpage


\include{1Introduction/scope}
\newpage


\section{LITERATURE REVIEW}
\newpage



\include{2Literaturereview/existing}
\newpage


\subsection{Proposed Systems}
Our proposed Deepfake Detection System is an online application created to aid users in identifying and mitigating the existence of deepfake content. It prioritizes offering robust deepfake detection capabilities to users. Users can take advantage of the system's deepfake detection tools, which enable them to submit images for analysis and detection of potential deepfake content. The system employs advanced algorithms and machine learning methods to accurately identify manipulated or artificially generated media. This assists users in recognizing and addressing the risks associated with deepfake content, such as spreading misinformation, perpetrating fraud, or violating privacy. The deepfake detection system strives to empower users by equipping them with the necessary resources to actively safeguard themselves and others against the potential negative consequences of encountering deepfakes. By leveraging cutting-edge algorithms, the system aids users in detecting and raising awareness about the presence of deepfakes, fostering a safer and more knowledgeable digital environment.
\newpage

\include{3FeasibilityStudy/feasibility_study}
\newpage


\include{4Methodology/methodology}



\begingroup

\let\clearpage\relax
\include{4Methodology/system_development_tools}
\include{4Methodology/functional_requirements}
\include{4Methodology/non_functional_requirements}
\endgroup

\newpage


\include{5BlockDiagrams/system_architecture}
\newpage


\include{5BlockDiagrams/use_case_diagram}
\newpage


\include{5BlockDiagrams/sequence_diagram}
\newpage


\include{5BlockDiagrams/dataFlow_diagram}
\newpage


\subsection{Activity Diagram}
\newpage



\include{6ExpectedOutcomes/expected_outcomes}
\newpage



\include{7Limitations/limitations}
\newpage

\include{8FutureEnhancements/future_enhancements}
\newpage


\include{References/references}
\end{document}