\begin{thebibliography}{99}
    % \begin{enumerate}
        \item\label{ref1} A. Rossler, D. Cozzolino, L. Verdoliva, C. Riess, J. Thies, M. Niessner, "FaceForensics++: Learning to Detect Manipulated Facial Images," IEEE Transactions on Information Forensics and Security, vol. 2, no. 4, pp. 1-4, 2019.

        \item\label{ref2} C. Vaccari and A. Chadwick, "Deepfakes and disinformation: exploring the impact of synthetic political video on deception, uncertainty, and trust in news," Social Media+ Society, vol. 6, no. 1, pp. 1-15, 2020.
        
        \item\label{ref3} X. Zhang, S. Karaman, and S.-F. Chang, "Detecting and simulating artifacts in GAN fake images," in 2019 IEEE International Workshop on Information Forensics and Security (WIFS), IEEE, 2019, pp. 23-30.
        
        \item\label{ref4} L. Guarnera, O. Giudice, C. Nastasi, and S. Battiato, "Preliminary forensics analysis of deepfake images," in 2020 AEIT International Annual Conference (AEIT), 2020, pp. 112-117.
        
        \item\label{ref5} "How can we combat the worrying rise in deepfake content?," World Economic Forum, Oct. 06, 2023. [Online]. Available: https://www.weforum.org/agenda/2023/05/how-can-we-combat-the-worrying-rise-in-deepfake-content/. [Accessed: August 3, 2023].
        
        \item\label{ref6} S. Agarwal, H. Farid, Y. Gu, M. He, K. Nagano, and H. Li, "Protecting World Leaders Against Deep Fakes," [Online]. Available: http://openaccess.thecvf.com/, May 22, 2021. [Accessed: August 3, 2023].
        
        \item\label{ref7} Y. Liu et al., "A Survey of Visual Transformers," IEEE Transactions on Neural Networks and Learning Systems, vol. 14, no. 3, pp. 789-801, March 2022.
        
        \item\label{ref8} Y. Liu, Y. Zhang, Y. Wang, F. Hou, J. Yuan, J. Tian, Y. Zhang, Z. Shi, J. Fan, and Z. He, "A Survey of Visual Transformers," ACM Transactions on Multimedia Computing, Communications, and Applications, vol. 8, no. 2, Article 15, 2021. [Online]. Available: https://doi.org/10.1145/XXXXXXX. [Accessed: August 3, 2023].
        
        \item\label{ref9} A. Vaswani et al., "Attention is all you need," in Advances in Neural Information Processing Systems, vol. 30, 2017.
        
        \item\label{ref10} B. Bahmei, E. Birmingham, and S. Arzanpour, "CNN-RNN and Data Augmentation Using Deep Convolutional Generative Adversarial Network for Environmental Sound Classification," IEEE Signal Processing Letters, vol. 29, pp. 682-686, 2022, doi: 10.1109/LSP.2022.3150258.
        
        \item\label{ref11} L. Papa, P. Russo, I. Amerini, and L. Zhou, "A survey on efficient vision transformers: algorithms, techniques, and performance benchmarking," Journal of LaTeX Class Files, vol. 14, no. 8, pp. 112-129, August 2015.
        
        \item\label{ref12} M. A. Arshed, A. Alwadain, R. Faizan Ali, S. Mumtaz, M. Ibrahim, A. Muneer, "Unmasking Deception: Empowering Deepfake Detection with Vision Transformer Network," Mathematics, vol. 11, p. 3710, 2023. [Online]. Available: https://doi.org/10.3390/math11173710. [Accessed: August 3, 2023].
        
        \item\label{ref13} A. Dosovitskiy et al., "An Image is Worth 16x16 Words: Transformers for Image Recognition at Scale," in International Conference on Learning Representations, 2021.
        
        \item\label{ref14} H. Touvron, M. Cord, M. Douze, F. Massa, A. Sablayrolles, and H. J´egou, “Training data-efficient image transformers and distillation through attention,” in Proceedings of the International Conference on Machine Learning (ICML), 2020.
        
        \item\label{ref15} N. Carion et al., "End-to-End Object Detection with Transformers," in Proceedings of the European Conference on Computer Vision (ECCV), pp. 213-229, 2020.
        
        \item\label{ref16} P. Shaw et al., "Self-Attention with Relative Position Representations," in Proceedings of the Conference of the North American Chapter of the Association for Computational Linguistics (NAACL), pp. 464-468, 2018.
        
        \item\label{ref17} M. S. Rana, M. N. Nobi, B. Murali, and A. H. Sung, "Deepfake Detection: A Systematic Literature Review," in IEEE Access, vol. 10, pp. 25494-25513, 2022, doi: 10.1109/ACCESS.2022.3154404.

        \item\label{ref18} H. Zhao, J. Jia, and V. Koltun, "Exploring self-attention for image recognition," in \emph{CVPR}, 2020.

        \item\label{ref19} B. Wu, C. Xu, X. Dai, A. Wan, P. Zhang, M. Tomizuka, K. Keutzer, and P. Vajda, "Visual transformers: Token-based image representation and processing for computer vision," \emph{arXiv}, 2020.
        
        \item\label{ref20} S. Qiao, H. Wang, C. Liu, W. Shen, and A. Yuille, "Weight standardization," \emph{arXiv preprint arXiv:1903.10520}, 2019.

        \item\label{ref21} A. Krizhevsky, "Learning multiple layers of features from tiny images," Technical Report, 2009.
        
        \item\label{ref22} D. P. Kingma and J. Ba, "Adam: A method for stochastic optimization," in \emph{ICLR}, 2015.
        
        \item\label{ref23} J.-B. Cordonnier, A. Loukas, and M. Jaggi, "On the relationship between self attention and convolutional layers," in \emph{ICLR}, 2020.
        
        \item\label{ref24} I. Bello, B. Zoph, Q. Le, A. Vaswani, and J. Shlens, "Attention augmented convolutional networks," in \emph{ICCV}, 2019.
        
        \item\label{ref25} J. L. Ba, J. R. Kiros, and G. E. Hinton, "Layer normalization," \emph{arXiv preprint arXiv:1607.06450}, 2016.
        
        \item\label{ref26} N. Srivastava, G. E. Hinton, A. Krizhevsky, I. Sutskever, and R. Salakhutdinov, "Dropout: A simple way to prevent neural networks from overfitting," \emph{Journal of Machine Learning Research}, vol. 15, no. 1, pp. 1929–1958, 2014.
        
        \item\label{ref27} K. He, X. Zhang, S. Ren, and J. Sun, "Deep residual learning for image recognition," \emph{arXiv preprint arXiv:1512.03385}, 2015.

        \item\label{ref27} H. Wang, S. Z. Li, and Y. Wang, "Face recognition under varying lighting conditions using self quotient image," in \emph{IEEE International Conference on Automatic Face and Gesture Recognition (AFGR)}, 2004, pp. 819-824.


        \item\label{ref28} M. Günther, R. Wallace, and S. Marcel, "An Open Source Framework for Standardized Comparisons of Face Recognition Algorithms," in \emph{Computer Vision - ECCV 2012. Workshops and Demonstrations}, LNCS, vol. 7585, pp. 547-556, 2012.
        
        \item\label{ref28} D. Zhang, J. Li, and Z. Shan, "Implementation of Dlib Deep Learning Face Recognition Technology," in \emph{2020 International Conference on Robots and Intelligent System (ICRIS)}, Sanya, China, 2020, pp. 88-91, doi: 10.1109/ICRIS52159.2020.00030.




% \end{enumerate}
\end{thebibliography}